### 2019-12-16 paper/introduction.tex
Introduction edited

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
 The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have a 
negative total temperature coefficient of reactivity 
\cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. However, graphite thermal expansion positively affect the 
core reactivity \cite{mathieu2006thorium}. The graphite expansion is not a 
dominating factor, thus core reactivity will decrease automatically when the 
core heats up \cite{li_optimization_2018}. MSR designs have a drain tank(s) to 
collect the liquid fuel in an emergency case. A freeze plug, which located 
under the core, melts when the temperature reaches a critical point. Then the 
fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.

@@

At the Beginning of Life (BOL), we must load the MSR with larger amount of fuel than that required to achieve criticality (necessary for long term core operation). This leads to excess reactivity at the BOL \cite{duderstadt650nuclear}. Additionally, during burnup, the online reprocessing and refueling leads to change the reactivity of the MSRs \cite{ashraf2019whole_core}. The most common procedure for reactor control is to insert or withdraw control rods with large neutron absorption cross section (e.g. boron and cadmium) \cite{duderstadt650nuclear}. Insertion of control rods introduces an amount of negative reactivity into the core. This negative reactivity helps to compensate the excess reactivity and adjust the power level of the core or even shut down the reactor in an emergency situation \cite{glasstone1967nuclear}. Therefore, we should estimate the reactivity worth of the control rods \cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}. The reactivity worth of control rods correlates with the interference (shadowing effects) between control rod clusters. \cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is used in control rods \cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. However, we may need to enrich the effective boron isotope ($^{10}$B) to reach the necessary absorptivity. Notably, the spatial self-shielding effect correlates with $^{10}$B concentration.
For example, B$_4$C enriched to 90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its absorption ability is about 2.3 times compared with natural B$_4$C. Additionally, issues related to helium gas release, swelling, melting risk, and high loss of the reactivity worth limit the B$_4$C lifespan \cite{guo2019optimized}.

Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the potential alternative absorbers in Generation-IV reactors such as hafnium-based materials and rare earth element oxides. These absorbers have high thermal conductivity, good resistance to neutron irradiation, and release almost no gas \cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ \cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated molten salt reactor. Recent studies on MSRs show that the excess reactivity at the beginning of the operation is quite large for many refueling scenarios \cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}. Adjusting fertile and fissile feed rates helps to control the reactivity of the SD-TMSR \cite{ashraf2019whole_core}. However, we should introduce a reliable safety system beside the online feed system to control the excess reactivity. Therefore, the main objective of our study is to introduce a new safety system based on control rods in the \gls{SD-TMSR} to control the reactivity during normal operation. Five different absorber materials are applied to study the main neutronics and safety parameters in the SD-TMSR. We focus on the control rod design, absorption ability, integral and differential control rod worths, shutdown margin of absorber materials, and shadowing effects at steady state calculation.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system in the GFR. They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes \cite{petrie1984keno} to calculate the reactivity worth and analyze the performance of this control system \cite{vcerba2017optimization}. Since no final geometry design of the control rods system is available for the SD-TMSR, \v{C}erba's methodology \cite{vcerba2017optimization}  helped us as a starting point of this analysis.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
 The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. However, temperature coefficient of reactivity for graphite 
is small but positive due to Doppler effect \cite{mathieu2006thorium, 
rykhlevskii_full-core_2017}. The graphite expansion is not a 
dominating factor, thus core reactivity will decrease automatically when the 
core heats up \cite{li_optimization_2018}. MSR designs have a drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

@@

At the Beginning of Life (BOL), we must load the MSR with larger amount of 
fuel than that required to achieve criticality (necessary for long term core 
operation). This leads to excess reactivity at the BOL 
\cite{duderstadt650nuclear}. Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2019whole_core}. The most common procedure 
for reactor control is to insert or withdraw control rods made of material 
with large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of  
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Notably, the spatial self-shielding 
effect correlates with $^{10}$B concentration. For example, B$_4$C enriched to 
90\% contains $^{10}$B 4.5 times larger than in natural B$_4$C, however, its 
absorption ability is about 2.3 times compared with natural B$_4$C. 
Additionally, issues related to helium gas release, swelling, melting risk, 
and high loss of the reactivity worth limit the B$_4$C lifespan 
\cite{guo2019optimized}.

Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas 
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Recent studies on MSRs showed that the excess reactivity 
at the beginning of the operation is quite large for many refueling scenarios 
\cite{ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
 Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2019whole_core}. However, we should introduce a 
reliable safety system beside the online feed system to control the excess 
reactivity. Therefore, the main objective of our study is to introduce a new 
fast reactivity control based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation. Five different absorber materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorber materials, and shadowing 
effects at steady state calculation.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
GFR. They utilized the MCNP5 \cite{briesmeister2000mcnptm} and KENO6 codes 
\cite{petrie1984keno} to calculate the reactivity worth and analyze the 
performance of this control system \cite{vcerba2017optimization}. Since no 
final geometry design of the control rods system is available for the SD-TMSR, 
\v{C}erba's methodology \cite{vcerba2017optimization}  helped us as a starting 
point of this analysis.
